### 2017-01-04 paper/evaluation.tex
Reworke content from RQ2

\Fix{to appear}

>>>>

We analyzed the distribution of time execution to investigate if most
of the cost is dominated by a small subset of test cases or if the
cost is nearly equally distributed. \Jbc{I shouldn't introduce
parallelization arguments here... May I just proceed to the
methodology?} \Fix{Regression tests that are well distributed may
benefit from parallelism since more tests executes at the same time
while the opposite scenario may require a different approach. In the
later scenario, executing tests in parallel may have insignificant
impact since a small subset of test cases dominates the execution.}

To evaluate how uniformly distribution the execution cost is among
test cases, we \Fix{...elaborate methodology...}

Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
different groups of subjects (\eg, test suites that are more equally
distributed than others) I think the results from this RQ should be
towards this direction}
